\prefacesection{Acknowledgements}
% \prefacesection creates a section called "Acknowledgements" as part of the preface section of the document.
%
%
This seminar is the outcome of my dedicated efforts, and I am grateful to several individuals and institutions for their direct and indirect support. Above all, I want to express my deepest gratitude to Almighty God for His endless blessings, guidance, and grace, without which this achievement would not have been possible.
% Introduction to the acknowledgements section, starting with a thank you to God for guidance and support.
%
I also express my sincere gratitude to my seminar guide, \textbf{Asst. Prof. Haritha H.}, for her continuous encouragement, invaluable guidance, motivation, and enthusiasm throughout my seminar. I deeply appreciate her support in terms of patience, time, and ideas, which made my seminar experience both stimulating and productive. \\[0.5cm]
% Acknowledgement and appreciation for the project guide, with \textbf{} used to bold the guide's name.
% \\[0.5cm] adds a line break and 0.5cm of vertical space after this paragraph for better readability.
%
My sincere gratitude goes to\textbf{ Dr. Anishin Raj M, Head of the Department} during my course period (2024-2025). I would also like to thank the seminar coordinator, \textbf{Assoc. Prof. Dr. Suja C Nair}, for critically assessing my work and providing valuable suggestions. I would like to acknowledge the Management of Muthoot Institute of Technology and Science for providing academic support to complete my seminar.\\[0.5cm]
% Acknowledges the Head of the Department and project coordinators for their support, with \textbf{} used to bold their names and titles.
% \\[0.5cm] adds a vertical space after this paragraph as well.
%
I feel fortunate to be surrounded by a supportive and cheerful group of fellow students in my daily work. I am sincerely grateful to all the members of S7 CSE B.\\\\
% Thanks fellow students from the class S7 CSE. 
% Double backslashes \\\\ create a larger line break to separate this sentence from the next section.
%
I would like to extend my heartfelt thanks to all the technical and non-technical staff, as well as the entire team of the Computer Science and Engineering Department, for creating a supportive environment. Additionally, I am grateful to everyone who has, knowingly or unknowingly, contributed to the successful completion of this seminar. I sincerely appreciate all of their help.
% Acknowledges both technical and non-technical staff, as well as others who contributed, directly or indirectly, to the completion of the seminar.
%
%
%
\vfill % This command pushes the following content (name) to the bottom of the page.
\hfill % This command aligns the following content (name) to the right of the page.
ALWIN YESUDAS
% The author's name is aligned to the right and placed at the bottom of the page.
%
% End of the chapter
%
%